Comparative effectiveness of BNT162b2 versus Moderna booster doses in England: preliminary report

### 2022-05-09 write-up/report.Rmd
Update report.Rmd

contrasts_overall %>%
  transmute(
    outcome_descr,
    subgroup_descr,
    subgroup_level_descr,
    n.atrisk=n.atrisk_0,
    persontime_0=label_number(1)(persontime_0/7), 
    persontime_1=label_number(1)(persontime_1/7),
    n.event_0, 
    n.event_1,
    riskCI_0 = paste0(label_number(0.01)(risk_0), " (", label_number(0.01)(risk.ll_0), "-", label_number(0.01)(risk.ul_0), ")"),
    riskCI_1 = paste0(label_number(0.01)(risk_1), " (", label_number(0.01)(risk.ll_1), "-", label_number(0.01)(risk.ul_1), ")"),
    kmrdCI = paste0(label_number(0.01)(kmrd), " (", label_number(0.01)(kmrd.ll), "-", label_number(0.01)(kmrd.ul), ")"),
    kmrrCI = paste0(label_number(0.01)(kmrr), " (", label_number(0.01)(kmrr.ll), "-", label_number(0.01)(kmrr.ul), ")"),
    irrCI =  paste0(label_number(0.01)(irr), " (", label_number(0.01)(irr.ll), "-", label_number(0.01)(irr.ul), ")"),
    #coxhrCI =  paste0(label_number(0.01)(kmrr), " (", label_number(0.01)(coxhr.ll), "-", label_number(0.01)(coxhr.ul), ")"),
  ) %>%
  group_by(outcome_descr) %>%
  mutate(
    # add indicator for row shading
    shade = cumsum((lag(subgroup_descr, 1, "")!=subgroup_descr)*1L),
    # remove repeat values of subgroup_level
    subgroup_descr = if_else(lag(subgroup_descr)==subgroup_descr & row_number()!=1, "", as.character(subgroup_descr)),
  ) %>%
  ungroup() %>%
  gt(groupname_col="outcome_descr") %>%
  cols_label(

>>>>

contrasts_overall %>%
  transmute(
    outcome_descr,
    subgroup_descr,
    subgroup_level_descr,
    n.atrisk=n.atrisk_0,
    persontime_0=label_number(1)(persontime_0/7), 
    persontime_1=label_number(1)(persontime_1/7),
    n.event_0, 
    n.event_1,
    riskCI_0 = paste0(label_number(0.01)(1-surv_0), " (", label_number(0.01)(1-surv.ul_0), "-", label_number(0.01)(1-surv.ll_0), ")"),
    riskCI_1 = paste0(label_number(0.01)(1-surv_1), " (", label_number(0.01)(1-surv.ul_1), "-", label_number(0.01)(1-surv.ll_1), ")"),
    kmrdCI = paste0(label_number(0.01)(kmrd), " (", label_number(0.01)(kmrd.ll), "-", label_number(0.01)(kmrd.ul), ")"),
    kmrrCI = paste0(label_number(0.01)(kmrr), " (", label_number(0.01)(kmrr.ll), "-", label_number(0.01)(kmrr.ul), ")"),
    irrCI =  paste0(label_number(0.01)(irr), " (", label_number(0.01)(irr.ll), "-", label_number(0.01)(irr.ul), ")"),
    #coxhrCI =  paste0(label_number(0.01)(kmrr), " (", label_number(0.01)(coxhr.ll), "-", label_number(0.01)(coxhr.ul), ")"),
  ) %>%
  group_by(outcome_descr) %>%
  mutate(
    # add indicator for row shading
    shade = cumsum((lag(subgroup_descr, 1, "")!=subgroup_descr)*1L),
    # remove repeat values of subgroup_level
    subgroup_descr = if_else(lag(subgroup_descr)==subgroup_descr & row_number()!=1, "", as.character(subgroup_descr)),
  ) %>%
  ungroup() %>%
  gt(groupname_col="outcome_descr") %>%
  cols_label(
